%!TEX root = ../my_thesis.tex
\section{Systematics}
\label{sec:systematics}

The identified systematic uncertainties are listed in
Table~\ref{tab:summarySyst} in decreasing order of their size.
Their quadratic sum is \Sfsyst~and \Sfbsyst~for $S_{f}$ and $S_{\bar f}$, respectively.
A description of each systematic effect  is given in the following subsections.
The ``fit biases'' are the residuals observed in the Monte Carlo bootstrap study discussed
in Sec.~\ref{sec:mcbootstrap}.

\begin{table}[htbp]
	\centering
	\caption{Systematic uncertainties on the \CP~parameters $S_{f}$ and
	$S_{\bar f}$.}
	\begin{tabular}{lcc}
		\toprule
		Source & $S_{f}$ & $S_{\bar f}$ \\
		\midrule
		uncertainty of $\Delta m$ & \num{0.0073} & \num{0.0061} \\
        fit biases & \num{0.0068} & \num{0.0018} \\
        background subtraction  & \num{0.0042} & \num{0.0023} \\
        flavour tagging calibration models & \num{0.0011} & \num{0.0015} \\
        flavour tagging efficiency asymmetries & \num{0.0012} & \num{0.0015} \\
        PIDK efficiencies & \num{0.0008} & \num{0.0008} \\
        acceptance model & \num{0.0007} & \num{0.0007} \\
        assumption $\DG=0$ & \num{0.0007} & \num{0.0007} \\
        assumption $C_f=-C_{\bar f}=1$ & \num{0.0006} & \num{0.0006} \\
        decay time resolution & \num{0.0012} & \num{0.0008} \\
		\midrule
		total systematic uncertainty & 0.0111 & 0.0073 \\
		\midrule
		statistical uncertainties & 0.0198 & 0.0199 \\
		\bottomrule
	\end{tabular}
	\label{tab:summarySyst}
\end{table}

\subsection{Systematic uncertainties from Gaussian constraints}
\label{sec:systFromConsts}
Systematic uncertainties due to external measurements used in the PDF
are accounted for through Gaussian constraints in the likelihood. These parameters are
the mixing frequency, $\Delta m$, and the \Bz~lifetime, $\tau$.
The fit has been repeated by fixing the Gaussian-constrained parameters to their central values,
in order to not propagate the uncertainty of these parameters to the statistical uncertainties of the fit.
The statistical uncertainties of $S_{f}$ and $S_{\bar f}$ with $\Delta m$ fixed are $0.0198$ and $0.0199$, respectively, whereas the statistical correlation is $0.6$.
Considering the difference in quadrature between the uncertainty from the nominal fit and that from this fit,
the systematic uncertainty due to $\Delta m$ are $0.0073$ and $0.0061$ for $S_{f}$ and $S_{\bar f}$, respectively.
The correlation between the systematic uncertainties due to $\Delta m$ on $S_{f}$ and $S_{\bar f}$ is $-1$, as described in Appendix~\ref{app:corrSyst}.
The fit with $\tau$ fixed shows that the systematics uncertainty due to this parameter is negligible.

Systematic uncertainty associated with the $\PIDK$ efficiencies (Table~\ref{tab:pideff})
are taken into account
in the mass fit by means of Gaussian constraints on these parameters (Sec.~\ref{sec:DataMassFit}).  The mass fit is repeated by neglecting these uncertainties in the Gaussian constraints.
Then, the time fit is performed with this new set of \emph{sWeights}. The difference
in quadrature between the uncertainty from this fit and that from the nominal fit gives the systematic due to the binning scheme in the
$\PIDK$ resampling, which is $0.0008$ for both $S_{f}$ and $S_{\bar f}$.
\input{06Systematics/fromToys}
\input{06Systematics/fromDataFits}
