\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\vskip0.2cm
I would like to express my deepest gratitude to my thesis advisor, Olivier Schneider, 
who supported my Ph.D. activity during four years. Despite his numerous
responsibilities and the little time left, he supervised my work with 
great attention to every detail and to my needs, still giving me the
opportunity to pursue and organise my research in complete freedom.
Also, I would like to thank
Aurelio Bay and Tatsuya Nakada for their trust in me
and for giving me the possibility to join the LPHE group at EPFL.
My gratitude also goes to the members of the jury who accepted to review my
work: C\'ecile H\'ebert, Tim Gershon, Niels Tuning and Mauro Doneg\`a.
A special thanks to Tim for the deep insight into the analysis during all the review stages of the paper,
and to Niels for the nice cooperation we had during LHCb operations, as well as for his support.   
This project would not have been possible without the incredible, wise and daily-based cooperation with 
Conor Fitpatrick and Mirco Dorigo, who helped me to master the art of analysing physics data
and supported me in many ways during these years. 
I had the pleasure to work with them and the privilege to be considered as a peer.
My gratitude extends also to Fred Blanc, Mark Tobin and Preema Pais:
working with them on the Silicon Tracker, down in the cavern or in the LHCb control room, was
fun and exciting.
A special thanks goes to the colleagues of the Technische Universit\"at of Dortmund, in particular to
Alex Birnkraut, Kevin Heinicke and Julian Wishahi, for the very nice and fruitful
cooperation. 
In these years, I had the incredible luck to work in a very friendly, open-minded and
collaborative environment thanks to my colleagues at LPHE, with whom I had a nice relationship beyond the working hours. 
The list is too long to report it here, but I would like to mention at least Rita Gian\`i, Violaine Bell\'ee, 
Zhirui Xu, Luca Pescatore, Pietro Marino, Maurizio Martinelli, Brice Maurin, Axel Kuonen, Olivier Girard, Maxime Schubiger,
Matthieu Marinangeli, Pavol Stefko, Guido Andreassi, Veronica Kirsebom, Vlado Macko, Maria Elena Stramaglia, 
Lino Ferreira Lopes, Guillaume Pietrzyk, Michel De Cian, Tara Nanut, Ana B\'arbara Rodrigues Cavalcante, 
Federico Redi, Jessica Prisciandaro, Albert Puig, Giovanni Veneziano, Ilya Komarov and Fred Dupertuis.
A special thanks goes to the LPHE secretaries Erika Luthi, Esther Hofmann and Corinne Craman, because they are the soul
of the lab, and without their support we (physicists) would be lost into the jungle of bureaucracy.  
I would like to thank all the people that I met at CERN, in particular those whom
I worked with closely or expressed their support for me under different circumstances:
Agnieszka Dziurda, Stefania Vecchi, Manuel Schiller, Vincenzo Vagnoni, Simon Akar, Bassem Khanji, Gloria Corti,
Concezio Bozzi, Wander Baldini, Carlos Abellan Beteta, MariaPilar Peco Regales and Barbara Storaci.  

My life would not be the same without my beloved wife, who supports (and stands) me unconditionally: thank you very much, Maria. 

Last but not least, thanks to my family (my parents Rosa and Alfredo, my sister Silvia, my aunts Pina and Elvira), to all the friends that I left in Italy (in particular, Giovanni Di Miceli, Adriano Baldeschi and Silvia Traversi), to my ancient athletic club (Virtus Campobasso, a real life trainer!), to my current triathlon club (Rushteam Ecublens, so nice to swim in Lac Leman and bike around Suisse Romande!) and to my math teacher in high school, Carla Mongillo.
